\section{Conclusions \& Discussion}
\label{sec:conclusions}

In this Letter, we examined Moosinesq convection.
We showed that convection inside moose produces interesting flow morphologies, and we noted that these flow complexities may have important implications for the evolution of moosive stars.

We examined a simple simulation with a Prantler number of unity; future work should lower the Prantler number, which would be more appropriate for stellar interiors \citep{garaud_2021} and could probably be achieved by studying a younger moose.
Moosive stars rotate rapidly, so future authors should study rotating convection at low Elkman number.
We suggest quantitative comparison to Rayleigh-B\'{e}nard convection through computation of the Mooselt number Moo, to understand how it compares to the classical Nusselt number Nu.

In this work we have focused on astrophysical applications, but the methods developed in this work may suggest a pathway toward unraveling the mysteries of other wildlife-related fluid phenomena, such as the powerful and mysterious otter of \cite{Schwab2021}\footnote{Also known as the Papaloizou-Pringle Patronus.}.
Lessons learned from this and future work on the Moosinesq approximation may also be of interest to those working in the yet-underexplored field of \textit{Goosinesq}\footnote{We leave the definition of this approximation to the reader's first thought.} convection.

The Boussinesq and Moosinesq approximations are formally valid when all length scales in the problem are small compared to the scale height and when compressibility is unimportant.
However, there are various applications in microbiology \citep{Ravetto2014} and wildlife ecology \citep[e.g.][]{Enright1963} wherein compressibility may be interesting.
Such studies have often focused on domains in which animal compressibility is more pronounced (i.e. deep-sea life).
However, motivated by a recent report of an unexpected occurrence of acute human compression and deformation via moose interaction \citep{Gudmannsson2018}, we recommend that the Moosinesq approximation be extended beyond the incompressible constraint studied here.



