% Preamble
\documentclass[onecolumn, twocolappendix]{aastex631}
%\documentclass[twocolumn]{aastex631}
\usepackage{natbib}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{epstopdf}
\usepackage{hyperref}
\usepackage{xcolor}

%%%% Custom commands
\newcommand{\yL}{\ensuremath{\mathcal{Y}_{\rm{L}}}}
\newcommand{\yS}{\ensuremath{\mathcal{Y}_{\rm{S}}}}
\newcommand{\justgrad}{\ensuremath{\nabla}}
\newcommand{\gradrad}{\ensuremath{\nabla_{\rm{rad}}}}
\newcommand{\gradad}{\ensuremath{\nabla_{\rm{ad}}}}
\newcommand{\gradC}{\ensuremath{\nabla_{\mathrm{C}}}}
\newcommand{\gradmu}{\ensuremath{\nabla_{\mu}}}
\newcommand{\gradL}{\ensuremath{\nabla_{\mathrm{L}}}}
\newcommand{\gradT}{\ensuremath{\nabla_{\mathrm{T}}}}
\newcommand{\Ro}{\ensuremath{\mathrm{R}_{0}}}
\newcommand{\delp}{\ensuremath{\delta_{\rm{p}}}}
\newcommand{\Fbot}{\ensuremath{F_{\rm{bot}}}}
\newcommand{\Ftot}{\ensuremath{F_{\rm{tot}}}}
\newcommand{\Frad}{\ensuremath{F_{\rm{rad}}}}
\newcommand{\Fconv}{\ensuremath{F_{\rm{conv}}}}
\newcommand{\Fcz}{\ensuremath{F_{\rm{cz}}}}
\newcommand{\mP}{\ensuremath{\mathcal{P}}}
\newcommand{\mD}{\ensuremath{\mathcal{D}}}
\newcommand{\dP}{\ensuremath{\delta_{\rm{p}}}}
\newcommand{\Lcz}{\ensuremath{L_{\rm{CZ}}}}
\newcommand{\mR}{\ensuremath{\mathcal{R}}}
\newcommand{\mS}{\ensuremath{\mathcal{S}}}
\newcommand\Pran{\ensuremath{\mathrm{Pr}}}
\newcommand{\brunt}{{Brunt-V\"{a}is\"{a}l\"{a}}}

\newcommand{\angles}[1]{\langle #1 \rangle}
\newcommand{\pd}[1]{\partial_{#1}}
\renewcommand{\vec}[1]{\boldsymbol{#1}}
\newcommand{\M}[1]{\mathbf{#1}}
\renewcommand{\dot}{\vec{\cdot}}
\renewcommand{\bar}[1]{\overline{#1}}
\newcommand{\grad}{\vec{\nabla}}
\newcommand{\cross}{\vec{\times}}
\newcommand{\laplacian}{\nabla^2}

\newcommand{\editone}[1]{\textcolor{orange}{#1}}

%%%% Journal preamble
\received{April 1, 2022}
\revised{April 1, 2022}
\accepted{???}
%\published{April 1, 2022}
\submitjournal{The Journal of Universal Rejection}

\shorttitle{Moosinesq Convection}
\shortauthors{Anders et al}

\begin{document}

%%%% Title and Abstract
\title{Moosinesq Convection in the Cores of Moosive Stars}
\author[0000-0002-3433-4733]{Evan H. Anders}
\affiliation{CIERA, Northwestern University, Evanston IL 60201, USA}
\author[0000-0002-4791-6724]{Evan B. Bauer}
\affiliation{Center for Astrophysics $\vert$ Harvard \& Smithsonian, 60 Garden St., Cambridge, MA 02138, USA}
\author[0000-0001-5048-9973]{Adam S. Jermyn}
\affiliation{Center for Computational Astrophysics, Flatiron Institute, New York, NY 10010, USA}
\author[0000-0001-8935-219X]{Benjamin P. Brown}
\affiliation{Department Astrophysical and Planetary Sciences \& LASP, University of Colorado, Boulder, CO 80309, USA}
\author[0000-0003-1651-9141]{Eric W. Hester}
\affiliation{Department of Mathematics, The University of California, Los Angeles, 520 Portola Plaza 90024, California, United States of America}
\author{Mindy Wilkinson}
\affiliation{Primum Terrae LLC}
\author[0000-0003-1012-3031]{Jared A. Goldberg}
\affiliation{Department of Physics, University of California, Santa Barbara, CA 93106, USA}
\author[0000-0002-4472-8517]{Samuel J. Van Kooten}
\affiliation{Southwest Research Institute, Boulder CO 80302, USA}
\author[0000-0002-7635-9728]{Daniel Lecoanet}
\affiliation{CIERA, Northwestern University, Evanston IL 60201, USA}
\affiliation{Department of Engineering Sciences and Applied Mathematics, Northwestern University, Evanston IL 60208, USA}

\correspondingauthor{Evan H. Anders}
\email{evan.anders@northwestern.edu}

\begin{abstract}
    Stars with masses $\gtrsim$ 1.1$M_\odot$ have core convection zones during their time on the main sequence.
    In these \emph{moosive stars}, convection introduces many uncertainties in stellar modeling.
    In this Letter, we build upon the Boussinesq approximation to present the first-ever simulations of \emph{Moosinesq convection}, which captures the complex geometric structure of the convection zones of these stars.
    These flows are bounded in a manner informed by the majestic terrestrial \emph{Alces alces} (moose) and could have important consequences for the evolution of these stars.
    We find that Moosinesq convection results in very interesting flow morphologies, and that the pun opportunities it provides are seemingly bottomless.
\end{abstract}
\keywords{TODO: something clever?}

%%%% Body of paper
\input{intro}

\input{methods}

\input{results}

\input{conclusions}

\begin{acknowledgments}
    We thank the Dedalus development team for creating an excellent tool that lets us create \sout{stupid} groundbreaking simulations like the one studied here.
EHA is funded as a CIERA Postdoctoral fellow and would like to thank CIERA and Northwestern University. 
This research was supported in part by the National Science Foundation under Grant No. PHY-1748958, and we acknowledge the hospitality of KITP during the Probes of Transport in Stars Program.
Computations were conducted with support from the NASA High End Computing (HEC) Program through the NASA Advanced Supercomputing (NAS) Division at Ames Research Center on Pleiades with allocation GID s2276.
The Flatiron Institute is supported by the Simons Foundation.
\end{acknowledgments}

\appendix

\input{appendix_history}

\input{appendix_mask}

\input{appendix_nondim}

\newpage
\bibliographystyle{aasjournal}
\bibliography{biblio}
\end{document}
